\chapter*{Acknowledgments}

First of all, I am most grateful to Prof.~Dr.~Jens Frahm, head of Biomedizinische NMR Forschungs GmbH am Max-Planck-Institut f\"{u}r biophysikalische Chemie, for offering me this invaluable opportunity to pursue my doctoral degree under his supervision, and providing me with inspiring advices, continuous support, and sufficient freedom for the development of scientific research. My doctoral thesis would have been impossible without him. More importantly, Prof.~Frahm is so knowledgeable that it has always been my great pleasure to listen to his keen insight into the cutting edge of MRI, to ask for potential solutions about tricky problems, to understand his elegant analysis, and of course, to follow his funny jokes.

I would also like to express my sincere appreciation to Drs.~Klaus-Dietmar Merboldt, Dirk Voit, Shuo Zhang, and Arun Joseph for advising my doctoral projects. Firstly, thanks very much to Dr.~Voit for always being patient when I ask questions about MRI pulse sequence programming and helping me with the design and implementation of multi-echo radial FLASH sequences. Secondly, the continuous support and data supply from Drs.~Merboldt and Joseph have encouraged me to work on the ``model-based reconstruction for real-time phase-contrast flow MRI" project, and it is of great honor for me to learn the physics of phase-contrast flow MRI from them. Thirdly, many thanks to Dr.~Zhang for getting me through my move from the USA to Germany and guiding me into the field of real-time MRI.

I have to thank all colleagues in BiomedNMR for many kind helps during the voyage of my doctoral thesis. In fact, I did not have any plan to study in Germany before accepted by Prof.~Frahm to start a doctoral project in his lab. However, it turns out that I really enjoy the academic environment in BiomedNMR. In the German word, ``Kann ich gar nicht sagen". Here, I learn from the colleagues about critical thinking and dialectic analysis. Especially, I would like to thank Dr.~Markus Untenberger for being a ``quality manager" in the adventures of several projects, Dr.~Oleksandr Kalentev (who has the nickname ``Sasha") for numerous discussions and joyful chats, Christian Holme (who actually has three first names) for sharing his fancy knowledge about computer science, and the Chinese colleagues (Zhongshuai Zhang and Xiaoqing Wang) for all kinds of support (e.g.~help relocate my furnitures without any payment). Finally, thank all the colleagues for organizing and joining various sport events -- soccer, kicker, badminton and table tennis. Particularly, I am really thankful to all the soccer teammates in the 2015 Sommerfest soccer tournament, Andy, Arijit, Jakob, Jost, Markus, Xiaoqing, and Zhongshuai. I truly can not imagine that I can still enjoy soccer matches after my madness toward soccer in middle school.

Next, I am grateful to my Bachelor advisor, Hong Zhang, Senior Engineer and Lecturer of Biomedical Engineering at Zhejiang University, for all his guidances in the theory of microprocessor and assembly language programming, and his advices on graduate studies. With his kind recommendation, I got the opportunity to visit Case Western Reserve University (CWRU), discuss with Dr.~Zhenghong Lee, and shake hands with Dr.~Mark Griswold, all of which left me a deep impression and encouraged me step into the field of medical imaging.

Further, I would like to thank my Master advisor, Dr.~Nan-Kuei Chen, Associate Professor at Brain Imaging \& Analysis Center (BIAC), Duke University. He was so generous that I had the opportunity to learn the basics of MRI and numerical simulations under his patient guidance. It was by understanding his excellent work on ``k-space energy spectrum analysis (\acs{KESA})" that I began to know about off-resonance effects in echo-planar imaging.

Being studying abroad for almost six years, I could have not gone through all the ups and downs without my dear parents, Tufu and Yanyu. You are always supporting me whenever and wherever it is. Plus, I am more than thankful to my beloved wife Kaikai and daughter Lezhi for teaching me how to be a mature man and bringing so many joys and hopes into my life! Without you, my lovely family, I can barely believe that I could have survived through the doctoral training period.

%Finally but not the last, I have to express my sincere apology toward my younger sister for missing the chances to accompany you during the past few years.

\begin{flushright}
  Zhengguo Tan \\
  Mar.~17, 2016
\end{flushright}

