
\section*{Journal Publications}
\begin{etaremune}
\item Zhengguo Tan, Volkert Roeloffs, Dirk Voit, Arun A Joseph, Markus Untenberger, K Dietmar Merboldt and Jens Frahm, \textbf{Model-based reconstruction for real-time phase-contrast flow MRI: Improved spatiotemporal accuracy}, \textit{Magnetic Resonance in Medicine}, 2016. \href{http://dx.doi.org/10.1002/mrm.26192}{DOI: 10.1002/mrm.26192}
\item Markus Untenberger$\dagger$, Zhengguo Tan$\dagger$, Dirk Voit, Arun A Joseph, Volkert Roeloffs, K Dietmar Merboldt, Sebastian Schaetz and Jens Frahm, \textbf{Advances in real-time phase-contrast flow MRI using asymmetric radial gradient echoes}, \textit{Magnetic Resonance in Medicine}, 2015. \href{http://dx.doi.org/10.1002/mrm.25696}{DOI: 10.1002/mrm.25696} ($\dagger$ Equal Contribution)
\end{etaremune}


\section*{Conference Contributions}
\begin{etaremune}
\item Zhengguo Tan, Volkert Roeloffs, Dirk Voit, Arun A Joseph, Markus Untenberger, K Dietmar Merboldt and Jens Frahm, \textbf{Model-based reconstruction for real-time phase-contrast flow MRI -- Improved spatiotemporal accuracy}, In \textit{Proceedings of the \nth{24} ISMRM}, Singapore, 2016. (power pitch)
\item Zhengguo Tan and Jens Frahm, \textbf{Model-based reconstruction for real-time phase-contrast flow MRI -- Improved spatiotemporal accuracy}, \textit{Departmental Poster Presentation to the Scientific Advisory Board (SAB) of MPIBPC}, 2015.
\item Zhengguo Tan, \textbf{Model-based reconstruction for real-time phase-contrast flow MRI}, talk on \textit{THIRD INFINITY}, G\"{o}ttingen, 2015.
\item Tom Hilbert, Tobias Kober, Tilman J Sumpf, Zhengguo Tan, Jens Frahm, Pavel Falkovskiy, Heiko Meyer, Rolf Bendl, Jean-Philippe Thiran and Reto Meuli, \textbf{MARTINI and GRAPPA -- When speed is taste}, In \textit{Proceedings of the \nth{22} ISMRM}, Milan, Italy, page 4077, 2014.
\item Zhengguo Tan, Dirk Voit and Jens Frahm, \textbf{Analytical multi-echo radial FLASH MRI simulation}, \textit{\nth{3} GGNB Science Day}, G\"{o}ttingen, 2013.
\item Zhengguo Tan and Nan-Kuei Chen, \textbf{Application of k-space energy spectrum analysis to artifact correction in PROPELLER MRI}, In \textit{Proceedings of the \nth{20} ISMRM}, Melbourne, Australia, page 2422, 2012.
\end{etaremune}

